Tempo and mode of promoter evolution as observed in the \textit{Paramecium aurelia} species complex

### 2020-07-31 manuscript.tex

Duplicate genes are a major source of evolutionary change (cite Moore and Puruggnan, 2006), and their evolutionary fates have long been a subject of intense study (cite several revent studies). The availability of high-quality genome assemblies and genome annotations has allowed us to investigate duplicate gene evolution in a variety of phylogenetic contexts (cite Gu et al., 2003 and others). However, while the fates of ortho-paralog pairs that arise through whole genome duplication (WGD) has been heavily studied (enter citations for \citep{Ohno:1970wm}; Wolfe and Shields, 1997, Force et al., 1999, others), the fates of \textit{cis}-regulatory regions of duplicate gene pairs is much less well-understood. (Discuss Haberer et al., Dong et al and Arsovski et al).

>>>>

Duplicate genes are a major source of evolutionary change (cite \citep{Ohno:1970wm} Moore and Puruggnan, 2006), and their evolutionary fates have long been a subject of intense study (reviewed in  The availability of high-quality genome assemblies and genome annotations has allowed us to investigate duplicate gene evolution in a variety of phylogenetic contexts (cite Gu et al., 2003 and others). However, while the fates of ortho-paralog pairs that arise through whole genome duplication (WGD) has been heavily studied (enter citations for \citep{Ohno:1970wm}; Wolfe and Shields, 1997, Force et al., 1999, others), the fates of \textit{cis}-regulatory regions of duplicate gene pairs is much less well-understood. (Discuss Haberer et al., Dong et al and Arsovski et al).
